The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-12-17 paper/mri_paper.tex
rm fig 2
new fig

\begin{figure}[h!]
\centering
\includegraphics[trim=6cm 3cm 3cm 0cm, scale=0.35]{slowfast.eps}
\caption{Cartoon illustrating fast and slow-moving variables (Equation \ref{scalings}).}\label{allorders_velocity}
\label{figscalings}
\end{figure}

@@

See Figure \ref{figscalings}. Note that these are the same scalings as apply to Rayleigh-B\'enard convection and hydrodynamic Taylor Couette flow. In analogy to these problems, we posit slow variation in both $Z$ and $T$. Each operator is expanded to reflect these scalings -- for instance, $\partial_z$ becomes $\partial_z + \epsilon\partial_Z$.

@@

Our analytic formulation is advantageous because we can now analyze the contributions of each fluid quantity at each order. This allows us to directly identify the source of saturation. Equation \ref{ampeq1} asymptotically approaches a value, so the system is clearly saturating, and our approach now allows us to quantify the individual contribution of each term. In Figure \ref{allorders_velocity}, we see significant fluid action in the second-order velocity plot. By contrast, the second-order magnetic field perturbations are two orders of magnitude smaller than the first-order perturbations (Figure \ref{allorders_Bfield}). It appears that the second-order velocity perturbations are instrumental in the saturation of the MRI. The likely mechanism is a reduction in the background shear.

>>>>

%\begin{figure}[h!]
%\centering
%\includegraphics[trim=6cm 3cm 3cm 0cm, scale=0.35]{slowfast.eps}
%\caption{Cartoon illustrating fast and slow-moving variables (Equation \ref{scalings}).}\label{allorders_velocity}
%\label{figscalings}
%\end{figure}

@@

%See Figure \ref{figscalings}. 
Note that these are the same scalings as apply to Rayleigh-B\'enard convection and hydrodynamic Taylor Couette flow. In analogy to these problems, we posit slow variation in both $Z$ and $T$. Each operator is expanded to reflect these scalings -- for instance, $\partial_z$ becomes $\partial_z + \epsilon\partial_Z$.

@@

Our analytic formulation is advantageous because we can now analyze the contributions of each fluid quantity at each order. This allows us to directly identify the source of saturation. Equation \ref{ampeq1} asymptotically approaches a value, so the system is clearly saturating, and our approach now allows us to quantify the individual contribution of each term. In Figure \ref{allorders_velocity}, we see significant fluid action in the second-order velocity plot. By contrast, the second-order magnetic field perturbations are two orders of magnitude smaller than the first-order perturbations (Figure \ref{allorders_Bfield}).

The role of the boundary layers changes with Pm. As Pm decreases, the width of the boundary layer becomes increasingly narrow (Figure \ref{u_secondorder_by_Pm}). The relative importance of the $u_y$ second order perturbation to the first order perturbation increases as well (CHECK, PLOT).

\begin{figure*}[h!]
\centering
\includegraphics[trim=6cm 0cm 6cm 0cm, scale=0.4]{u_secondorder_by_Pm_2.eps}
\caption{(Placeholder) The evolution of the second-order velocity perturbations by Pm.}\label{allorders_velocity}
\label{u_secondorder_by_Pm}
\end{figure*}

It appears that the second-order velocity perturbations are instrumental in the saturation of the MRI. The likely mechanism is a reduction in the background shear.
